TBD

### 2016-10-18 paper.tex
lincal

\newcommand{\bz}{\bmath{z}}
\newcommand{\bA}{\bmath{A}}
\newcommand{\bB}{\bmath{B}}
\newcommand{\bC}{\bmath{C}}
\newcommand{\bE}{\bmath{E}}
\newcommand{\bF}{\bmath{F}}
\newcommand{\bG}{\bmath{G}}
\newcommand{\br}{\bmath{r}}
\newcommand{\bg}{\bmath{g}}
\newcommand{\bd}{\bmath{d}}
\newcommand{\bv}{\bmath{v}}
\newcommand{\bn}{\bmath{n}}
\newcommand{\by}{\bmath{y}}
\newcommand{\bJ}{\bmath{J}}
\newcommand{\bD}{\bmath{D}}
\newcommand{\bH}{\bmath{H}}
\newcommand{\bN}{\bmath{N}}
\newcommand{\bM}{\bmath{M}}
\newcommand{\bO}{\bmath{O}}
\newcommand{\bP}{\bmath{P}}
\newcommand{\bQ}{\bmath{Q}}
\newcommand{\bI}{\bmath{I}}
\newcommand{\ba}{\bmath{a}}
\newcommand{\bb}{\bmath{b}}
\newcommand{\bx}{\bmath{x}}
\newcommand{\bp}{\bmath{p}}
\newcommand{\bmJ}{\bmath{\mathcal{J}}}
\newcommand{\bzero}{\bmath{0}}
%\newcommand{\bvarrho}{\bmath{\varrho}}
%\newcommand{\bnu}{\bmath{\nu}}
%\newcommand{\bvarphi}{\bmath{\varphi}}
\newcommand{\conj}[1]{\overline{#1}}

@@

\section{LINCAL}
%Assume that $\eta_p,\eta_q,\widetilde{\eta}_{\phi_{pq}},\varphi_p,\varphi_q$ and $\widetilde{\varphi}_{\phi_{pq}}$ are real valued variables.
We can rewrite Eq.~\eqref{eq:vis_red_vec} to
\begin{equation}
\label{eq:lincal_vec}
\bd = \bv(\bvarrho) + \bn, 
\end{equation}
where 
\begin{equation}
\left [ \bv(\bvarrho) \right ]_{\alpha_{pq}} = e^{\eta_p - i \varphi_p} e^{\widetilde{\eta}_{\phi_{pq}}- i \widetilde{\varphi}_{\phi_{pq}}} e^{\eta_q + i \varphi_q},
\end{equation}
\begin{equation}
 \bvarrho = 
\begin{bmatrix}
\bmath{\eta} \\
\bvarphi \\
\widetilde{\bmath{\eta}} \\
\widetilde{\bvarphi}
\end{bmatrix},
\end{equation}
with
\begin{align}
 \bmath{\eta} &= [\eta_1, \eta_2,\cdots \eta_N]^T\nonumber\\
 \bmath{\varphi} &= [\varphi_1, \varphi_2,\cdots \varphi_N]^T\nonumber\\
 \widetilde{\bmath{\eta}} &= [\widetilde{\eta_1}, \widetilde{\eta_2},\cdots \widetilde{\eta_L}]^T\nonumber\\
 \widetilde{\bmath{\varphi}} &= [\widetilde{\varphi_1}, \widetilde{\varphi_2},\cdots \widetilde{\varphi_L}]^T.
\end{align}
Moreover, $\bmath{\eta},~\bvarphi,~\widetilde{\bmath{\eta}}$ and $\widetilde{\bvarphi}$ are real valued vectors.
If we Taylor expand Eq.~\eqref{eq:lincal_vec} we obtain
\begin{align}
\bd &= \bv + \Delta \bvarrho \bmJ + \bn\\
\br &= \Delta \bvarrho \bmJ + \bn,
\end{align}
where
\begin{equation}
\label{eq:jac_upper_lincal}
\bmJ = \begin{bmatrix}
       \bN & \bM 
       \end{bmatrix}
\end{equation}

\begin{align}
 \left [ \bd \right]_{\alpha_{pq}} &= d_{pq}, & \left [ \bv \right ]_{\alpha_{pq}} &= g_p y_{\phi_{pq}} \conj{g_q}\nonumber\\
 \left [ \bn \right ]_{\alpha_{pq}} &= n_{pq}. &  &\label{eq:lincal_definitions}
\end{align}

A possible approach one can use to solve the unknowns in Eq.~\eqref{eq:lincal} is to write down the Taylor expansion of the first term of the right hand side of Eq.~\eqref{eq:lincal} around some 
initial fiducial guess of $\eta_p,\eta_q,\widetilde{\eta}_{\phi_{pq}},\varphi_p,\varphi_q$ and $\widetilde{\varphi}_{\phi_{pq}}$, which we denote with 
$\eta_p^0,\eta_q^0,\widetilde{\eta}_{\phi_{pq}}^0,\varphi_p^0,\varphi_q^0$ and $\widetilde{\varphi}_{\phi_{pq}}^0$, and then to solve the perturbations from this 
initial guess that minimize the difference between the right and left hand side of Eq.~\eqref{eq:lincal}. Once the perturbation values 
have been computed it is trivial to obtain an estimate of $g_i$, $g_j$ and $y_{\phi_{ij}}$.

If we Taylor expand the first term on the right hand side of Eq.~\eqref{eq:lincal} around a fiducial initial guess we obtain
\begin{equation}
\label{eq:taylor_expansion}
d_{pq} = v_{pq}^0[1+\Delta \eta_p + \Delta \eta_q + i \varphi_p - i \Delta \varphi_q + \Delta \widetilde{\eta}_{\phi_{pq}} + i\Delta \widetilde{\eta}_{\phi_{pq}}] + n_{pq}, 
\end{equation}
where
\begin{equation}
v_{pq}^0 = e^{\eta_p^0 - i \varphi_p^0} e^{\widetilde{\eta}_{\phi_{pq}}^0 - i \widetilde{\varphi}_{\phi_{pq}}^0} e^{\eta_q^0 + i \varphi_q^0}, 
\end{equation}
and $\eta_p^0,\eta_q^0,\widetilde{\eta}_{\phi_{pq}}^0,\varphi_p^0,\varphi_q^0$ and $\widetilde{\varphi}_{\phi_{pq}}^0$ respectively denote the initial guess for $\eta_p,\eta_q,\widetilde{\eta}_{\phi_{pq}},\varphi_p,\varphi_q$ and $\widetilde{\varphi}_{\phi_{pq}}$.
Eq.~\eqref{eq:taylor_expansion} can be used to construct the following linear system
\begin{equation}
\breve{\br} = \bJ\Delta\widehat{\bz}, 
\end{equation}
where 
\begin{equation}
\left [ \breve{\br} \right ]_{\alpha_{pq}} = d_{pq}-v_{pq}^0, 
\end{equation}
\begin{equation}
\label{eq:jac_lincal}
\bJ = \begin{bmatrix}
      \bN & \bM\\
      \conj{\bN} & \conj{\bM}
      \end{bmatrix}
\end{equation}
and
\begin{equation}
\Delta\widehat{\bz} = 
\begin{bmatrix}
\Delta \bmath{\eta} \\
\Delta \bmath{\varphi} \\
\Delta \widetilde{\bmath{\eta}} \\
\Delta \widetilde{\bmath{\varphi}},
\end{bmatrix}
\end{equation}
with
\begin{align}
 \Delta \bmath{\eta} &= [\Delta \eta_1,\Delta \eta_2,\cdots \Delta \eta_N]^T\nonumber\\
 \Delta \bmath{\varphi} &= [\Delta \varphi_1,\Delta \varphi_2,\cdots \Delta \varphi_N]^T\nonumber\\
 \Delta \widetilde{\bmath{\eta}} &= [\Delta \widetilde{\eta_1},\Delta \widetilde{\eta_2},\cdots \Delta \widetilde{\eta_N}]^T\nonumber\\
 \Delta \widetilde{\bmath{\varphi}} &= [\Delta \widetilde{\varphi_1},\Delta \widetilde{\varphi_2},\cdots \Delta \widetilde{\varphi_N}]^T.
\end{align}

Furthermore, 
\begin{equation}
\bN = \begin{bmatrix}
      \bN_1 & \bN_2 
      \end{bmatrix},
\end{equation}
with 
\begin{align}
[\bN_1]_{\alpha_{pq},j} &= \frac{\partial v_{pq}}{\partial \eta_j} {\bigg |}_{\widehat{\bz}=\widehat{\bz}^0}\\
&= (\delta_{p}^{j}\vee\delta_{q}^{j}) v_{pq}^0,
\end{align}
and
\begin{align}
 [\bN_2]_{\alpha_{pq},j} &= \frac{\partial v_{pq}}{\partial \varphi_j} {\bigg |}_{\widehat{\bz}=\widehat{\bz}^0}\\
 &= (-1)^{\delta_{q}^{j}}i(\delta_{p}^{j}\vee\delta_{q}^{j}) v_{pq}^0. 
\end{align}

Moreover,
\begin{equation}
\bM = \begin{bmatrix}
      \bM_1 & \bM_2 
      \end{bmatrix},
\end{equation}
with
\begin{align}
[\bM_1]_{\alpha_{pq},j} &= \frac{\partial v_{pq}}{\partial \widetilde{\eta}_j} {\bigg |}_{\widehat{\bz}=\widehat{\bz}^0}\\
&=  \delta_{\phi_{pq}}^{j} v_{pq}^0,
\end{align}
and
\begin{align}
[\bM_2]_{\alpha_{pq},j} &= \frac{\partial v_{pq}}{\partial \widetilde{\varphi}_j} {\bigg |}_{\widehat{\bz}=\widehat{\bz}^0}\\
&= i\delta_{\phi_{pq}}^{j} v_{pq}^0,
\end{align}

>>>>

\newcommand{\bz}{\bmath{z}}
\newcommand{\bA}{\bmath{A}}
\newcommand{\bB}{\bmath{B}}
\newcommand{\bC}{\bmath{C}}
\newcommand{\bE}{\bmath{E}}
\newcommand{\bF}{\bmath{F}}
\newcommand{\bG}{\bmath{G}}
\newcommand{\br}{\bmath{r}}
\newcommand{\bg}{\bmath{g}}
\newcommand{\bd}{\bmath{d}}
\newcommand{\bv}{\bmath{v}}
\newcommand{\bn}{\bmath{n}}
\newcommand{\by}{\bmath{y}}
\newcommand{\bJ}{\bmath{J}}
\newcommand{\bD}{\bmath{D}}
\newcommand{\bH}{\bmath{H}}
\newcommand{\bN}{\bmath{N}}
\newcommand{\bM}{\bmath{M}}
\newcommand{\bO}{\bmath{O}}
\newcommand{\bP}{\bmath{P}}
\newcommand{\bQ}{\bmath{Q}}
\newcommand{\bR}{\bmath{R}}
\newcommand{\bI}{\bmath{I}}
\newcommand{\ba}{\bmath{a}}
\newcommand{\bb}{\bmath{b}}
\newcommand{\bx}{\bmath{x}}
\newcommand{\bp}{\bmath{p}}
\newcommand{\bmJ}{\bmath{\mathcal{J}}}
\newcommand{\bzero}{\bmath{0}}
%\newcommand{\bvarrho}{\bmath{\varrho}}
%\newcommand{\bnu}{\bmath{\nu}}
%\newcommand{\bvarphi}{\bmath{\varphi}}
\newcommand{\conj}[1]{\overline{#1}}

@@

\section{LINCAL}
%Assume that $\eta_p,\eta_q,\widetilde{\eta}_{\phi_{pq}},\varphi_p,\varphi_q$ and $\widetilde{\varphi}_{\phi_{pq}}$ are real valued variables.
We can rewrite Eq.~\eqref{eq:vis_red_vec} to
\begin{equation}
\label{eq:lincal_vec}
\bd = \bv(\bvarrho) + \bn, 
\end{equation}
where 
\begin{align}
\left [ \bv(\bvarrho) \right ]_{\alpha_{pq}} &= e^{\eta_p - i \varphi_p} e^{\widetilde{\eta}_{\phi_{pq}}- i \widetilde{\varphi}_{\phi_{pq}}} e^{\eta_q + i \varphi_q}\\
&= v_{pq},
\end{align}
and
\begin{equation}
\bvarrho = 
\begin{bmatrix}
\bmath{\eta} \\
\bvarphi \\
\widetilde{\bmath{\eta}} \\
\widetilde{\bvarphi}
\end{bmatrix},\qquad
\begin{aligned}
\bmath{\eta} &= [\eta_1, \eta_2,\cdots \eta_N]^T\\
 \bmath{\varphi} &= [\varphi_1, \varphi_2,\cdots \varphi_N]^T\\
 \widetilde{\bmath{\eta}} &= [\widetilde{\eta_1}, \widetilde{\eta_2},\cdots \widetilde{\eta_L}]^T\\
 \widetilde{\bmath{\varphi}} &= [\widetilde{\varphi_1}, \widetilde{\varphi_2},\cdots \widetilde{\varphi_L}]^T
\end{aligned}.
\label{eq:help}
\end{equation}
Note that the vectors $\bmath{\eta},~\bvarphi,~\widetilde{\bmath{\eta}}$ and $\widetilde{\bvarphi}$ are real valued.

The first oreder Taylor expansion of Eq.~\eqref{eq:lincal_vec} around the fiducial point $\bvarrho_0$ is equal to
\begin{equation}
\label{eq:d_lin}
\bd = \bv_0 + \bmJ_0 \Delta \bvarrho  + \bn.
\end{equation}
Calculating the residual and dropping the reference to a specific fiducial point, we obtain 
\begin{equation}
\label{eq:r_lin}
\br = \bd - \bv = \bmJ \Delta \bvarrho + \bn.
\end{equation}
Moreover,
\begin{equation}
\label{eq:jac_upper_lincal}
\bmJ = \begin{bmatrix}
       \bN & \bM 
       \end{bmatrix},
\end{equation}
where
\begin{align}
\bN &= \begin{bmatrix} \bO & \bP \end{bmatrix}, & \bM &= \begin{bmatrix} \bQ & \bR \end{bmatrix}, 
\end{align}

\begin{equation}
 [\bO]_{\alpha_{pq},j} =  \frac{\partial v_{pq}}{\partial \eta_j} = \begin{cases} 
    v_{pq} &\textrm{if}~(p=j)~\textrm{or}~(q=j)\\
    0 & \textrm{otherwise}
   \end{cases},
\end{equation}

\begin{equation}
 [\bP]_{\alpha_{pq},j} =  \frac{\partial v_{pq}}{\partial \varphi_j} = \begin{cases}
                                                                        i v_{pq} &\textrm{if}~ p=j\\
                                                                        -i v_{pq} &\textrm{if}~ q=j \\
                                                                        0 & \textrm{otherwise} 
                                                                       \end{cases}
\end{equation}

\begin{equation}
 [\bQ]_{\alpha_{pq},j} =  \frac{\partial v_{pq}}{\partial \widetilde{\eta}_j} = \begin{cases} 
    v_{pq} &\textrm{if}~\phi_{pq}=j\\
    0 & \textrm{otherwise}
   \end{cases},
\end{equation}

\begin{equation}
 [\bR]_{\alpha_{pq},j} =  \frac{\partial v_{pq}}{\partial \widetilde{\varphi}_j} = \begin{cases} 
    i v_{pq} &\textrm{if}~\phi_{pq}=j\\
    0 & \textrm{otherwise}
   \end{cases}.
\end{equation}

The augmented residual is equal to 
\begin{equation}
\breve{\br} = \bJ \Delta \bvarrho + \bn, 
\end{equation}

where $\breve{\br} = [r,\conj{r}]^T$ and 
\begin{equation}
\bJ =
\begin{bmatrix}
 \bmJ\\
 \conj{\bmJ}
\end{bmatrix}.
\end{equation}
